A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-14 EvoPar2017/paper.Rnw
Drawing some early conclusions

>>>>

The graph that plots the time to solution of every instance of the
experiment vs. entrop is shown in \ref{fig:entropy}. There is a clear
trend towards experiments with lower entropy taking more time and
experiments with higher entropy taking more time, which indeed can be
statistically fit to a linear model. This dependence on entropy is
much clearer than the assumed dependence on the number of users, which
is represented in the graph by dot color, and even the number of PUTs
or contributions, which is represented by dot size. You can see a
clearly blue and big dot, meaning more than 40 different IPs
participating and around 1500 PUTs in the high end of the graph,
showing that it took the longest to find the solution. On the other
hand, clearly red and small dots are on the lowest end of the graph,
indicating that it took a short time to find the solution as long as
the entropy is high.

This is a very significant result which has many implications on
volunteer computing experiment design, and is clearly something that
has to do more with the fact that we are dealing with an evolutionary
algorithm where creating and maintaining diversity is an important
part of its exploration component, than with the fact that it is a
volunteer computing experiment. This is why we claim that volunteer
computing setups are, in some cases, a better option than synchronous
and distributed implementations with a similar computing capability,
because if diversity is kept high, the performance achieved can be
much better than in similar synchronous and parallel experiments.
